A free/open-source Kazakh-Tatar machine translation system

### 2013-07-01 paper/paper.tex
actually this is what we submitted
list of minor fixes ''The contents of Sections 2 and 3 do not correspond to the description given in Section 1.''

The paper will be laid out as follows: Section~\ref{sec:prev}\ gives a brief
description of the two languages; Section~\ref{sec:lang}\ gives a short review
of some previous work in the area of Turkic--Turkic language translation and compares the grammar of Kazakh and Tatar;
Section~\ref{sec:sys}\ describes the system and the tools used to construct it;
Section~\ref{sec:eval}\ gives a preliminary evaluation of the system; and
finally Section~\ref{sec:conc}\ describes our aims for future work and some
concluding remarks.

@@

An MT system between Tatar and Kazakh is potentially of great use to the language communities.  Direct MT can save time and money over going through e.g.\ Russian (and the system is much easier to develop).  Some accompanying language resources (e.g.,\ morphol.\ analysers, disambiguators) can be repurposed.

>>>>

The paper will be laid out as follows: Section~\ref{sec:prev}\ gives a short review of some previous work in the area of Turkic--Turkic language machine translation; Section~\ref{sec:lang} introduces Kazakh and Tatar and compares their grammar; 
Section~\ref{sec:sys}\ describes the system and the tools used to construct it;
Section~\ref{sec:eval}\ gives a preliminary evaluation of the system; and
finally Section~\ref{sec:conc}\ describes our aims for future work and some
concluding remarks.

@@

An MT system between Tatar and Kazakh is potentially of great use to the language communities.  Direct MT can save time and money over going through e.g.\ Russian (and the system is much easier to develop).  Some accompanying language resources (e.g.,\ morphol.\ analysers, disambiguators) can also be repurposed.
